---
title: "Star Digital Causal Analysis"
author: "Hao Cheng"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(readxl)
library(car)
library(reshape)
library(dplyr)
data <- read_excel("M347SS-XLS-ENG.xls")
data$test<-as.factor(data$test)
```
# Background Introduction
Star Digital, a multi-channel video service provider would like to know whether it should invest more on online advertising, especially on banner advertising.Therefore, they conducted an experiment to understand the incremental impact of advertising on sales. They randomly assigned consumers into test and control groups based on exposure of ads from a charity organization and Start Digital. The goal is to analyze the effectiveness of experiment, increase purchase frequency, and find the target sites for budget management.

# Experiment Design
## (a) Treatment and control group

Treatment variable: whether the software places campaign ads to customers or not

Treatment group: 90% of customers who were shown Star Digital Ads

Control group: 10% of customers who were shown charity organization ads

## (b) The unit of analysis
Customers viewing online advertisements

## (c) Testing method
A/B testing

# Threat of causal inference
## 1. Omitted variable bias:

The customer personal information such as gender and age might be omitted. It is likely that these factors are correlated to the final purchasing. For example, younger generation is more likely to subscribe because they addict more to social media and networks.

## 2. Simultaneity bias:

In some cases, not only impressions influence on purchase decision, dependent variable(purchase) can affect independent variable(impressions). For instance, consumers may be impressed more on specific sites after subscription.

## 3. Measurement error:

We cannot accurately count and check if users really view the ads, since some extension tools might block the ads.

## 4. Selection bias:

There is no evidence about which sample of customers are selected in the experiment. It is possible that consumers in the experiment are mostly low financial level and cannot afford the subscription.

# Exploratory Data Analysis
This dataset includes 1 id column, 6 numerical independent variables (imp_1 ~ imp_6), 1 binary treatment variable (test), and 1 binary dependent variable (purchase).  
We conduct data processing to view the statistics and check the assumption.

## 1. Descriptive summary
```{r}
summary(data[3:8])
```

## 2. Check missing values
```{r}
sum(is.na(data))
```

## 3. Data Transformation
We combine the numbers of impressions that the consumer saw at website1 through 5, and all websites.
```{r}
data=data %>% mutate(imp1to5=imp_1+imp_2+imp_3+imp_4+imp_5)
data=data %>% mutate(imp_all=imp_1+imp_2+imp_3+imp_4+imp_5+imp_6)
```


# Before experiments

## 1. Randomization Check
We conducted t.test to see whether the control and treatment groups have the similar average number of imp_1to5 and imp_6. It shows that p-values of both imp_1to5 and imp6 are larger than 0.05, which means the numbers of impression 1 to 5 and impression 6 are not different between the control and treatment groups. That is, the experiment is successfully randomized.
```{r}
# p-value = 0.5188 > alpha(0.05), do not reject H0.
t.test(imp1to5 ~ test,data=data)

# p-value = 0.6661 > alpha(0.05), do not reject H0.
t.test(imp_6 ~ test,data=data)

# p-value = 0.8987 > alpha(0.05), do not reject H0.
t.test(imp_all ~ test,data=data)
```

## 2. Power Test
We check whether the sample size is less than or larger than the minimum required, we use alpha=0.05 and beta=0.2. If we would like to detect 0.1% change in purchase rate, we need at least 174 samples in each group. For this case, we have more than 20000 samples in treatment and more than 2000 samples in control group. Therefore, it is an overpowered study.

```{r}
# treatment
treat<-filter(data,test==1)
p1<-mean(treat$purchase)
n1<-nrow(treat)
s1<-sqrt(p1*(1-p1)/n1)

# control
control<-filter(data,test==0)
p2<-mean(control$purchase)
n2<-nrow(control)
s2<-sqrt(p2*(1-p2)/n2)

power.t.test(delta = 0.001,sd=s1, sig.level = 0.05, type = 'two.sample', power = 0.8, alternative = 'two.sided')
```

# Three experiments

## 1. The Effectiveness of Online Advertising for Star Digital
We performed t-test to check if the campaign ads (treatment) affects the purchase (dependent variables).

```{r}
# p-value = 0.06139 > 0.05(alpha), do not reject H0
t.test(purchase~test, data = data)
```
The p-value is a small number (although slightly greater >5%), but we conclude that it is marginally significant. This implies that the test group have positive effect on purchase. Therefore, the ads are effective.

## 2. Relationship between Impressions and Purchase
We use simple linear regression models on the treatment group to find out whether the change in number of impressions would result in changes of purchase. 

```{r}

summary(lm(purchase ~ test*imp_all, data))
```
Looking at the effect of total impressions on the odds of purchase, we see a very significant p-value(3.49e-10), much lower than 0.05. This means that there is evidence that the total number of ad impressions for each consumer effects whether they make a purchase at Star Digital or not. The coefficient of the total impression term is 0.0025937, which means that there is around 0.25% increase in purchasing  at Star Digital if incrase 1 impression in the control group. This indicates that more online activity increases the frequency of purchasing at Star Digital, regardless of whether they are seeing Star Digital ads.

As for treatment group, the p-value for the interaction between being in the treatment group and total impressions is under 0.05 (0.0188). This means that there is evidence that there is difference in the effect of an additional ad impression between the treatment and control group. And the coefficient on the interaction term is around 0.1%, indicating increasing in purchase odds for the control group, consumers in the treatment group are expected to have an additional 0.1% increase of purchasing at Star Digital.

In conclusion, it appears that a higher frequency of advertising does increase the probability of purchase.

## 3. Choosing between Website 6 or Websites 1 through 5

We use simple linear regression models on the treatment group to compare the average impact on site1 to site 5 and that on site 6 purchase.
Then, We used ROI to make business decision. 
ROI= ((Value of Purchase * Increase of Purchase) - Cost of Impression) / Cost of Impression

```{r}
summary(lm(purchase ~ test*imp1to5 , data ))
summary(lm(purchase ~ test*imp_6, data))
```

The p-value for both [test:imp1to5] and [test:imp_6] are all smaller than 0.05, indicating that there is evidence that there is difference in the effect of an additional ad impression between the treatment and control group for "site1 to site5" and "site 6".

```{r}
ROI_site1to5 = ((1200 * 0.0007301) - (25 / 1000)) / (25 / 1000)
ROI_site1to5
```


```{r}
ROI_site6 = ((1200 * 0.0014738) - (20 / 1000)) / (20/1000)
ROI_site6
```

In conclusion, Star Digital should put its advertising dollars in Site 6, because sit 6 has higher ROI.
